Contracts for unions and intersections are hard for Nickel

### 2021-05-07 paper.tex
Started survey on other papers

>>>>

The papers that previously researched union and intersection
as dynamic checks have, in our eyes, different shortcomings
that makes them suboptimal solutions.

Starting with the Keil and Thiemann work \cite{KeilThiemannUnionIntersection},
they noticed that, since union contracts should share information between
different application contexts, while intersection contracts should behave
independently between each application context, the system becomes much
simpler if every contract gets transformed into a union of intersections
of other contracts, by using the usual De Morgan laws,
and then eagerly opening up unions, but postponing intersection
contracts as much as possible.
\todo{This assumes the difficulty has been previously explained}

This straightforward solutions makes composing the Keil and Thiemann
system with other existing systems more difficult; in the words
of Williams, Morrison, and Wadler:
"(...) the monitoring semantics for contracts of intersection and union types given by Keil
and Thiemann are not uniform. (...) If uniformity helps composition, then
special cases can hinder composition."\cite{RootCauseOfBlame}

Another difficult issue Keil and Thiemann were able to solve, is the
fact that flat contracts and intersection do not usually play nice
together.
They provide two different set of rules for their calculus,
the first one is non deterministic, which purpose is to provide
semantics that are simple to understand.
The second one is a deterministic set of rules, that are intended
to be simply to implement. These semantics need to perform operations
on the evaluation context, to decide whether or not to evaluate
a given contract.

We see two problems here, a minor one is the fact that two different
semantics need to be defined, which translates either to a difficult
to implement or a difficult to understand system. A second, major one,
is the dependency added over the evaluation context, since, again,
it makes composing this, with other features desired on programming languages,
difficult, or even impossible (as the case with common subexpression elimination).

Williams, Morrison, and Wadler, take a different approach on flat contracts,
they are completely forbidden in their system, explicitly to not encounter
the previously mentioned issue.
This restriction goes against what is usually expected from dynamic checks:
validation of data, and not just inclusion on types, is an expected
feature of these systems.

\todo{Monitoring sound problem}
